---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Why qckitalign?

Although quality control of fastq files are well established, there are far fewer quality control packages for reference alignment, despite QC being important at all levels of a bioinformatics pipeline. qckitalign is part of the R qckit suite by the Computational Biology Core at Brown University, and aims to provide a relatively complete R package for (reference) alignment quality control. It's built on SeqAn, benchmarked with RBenchmark (todo: benchmark) visualized with ggplot, and contains associated modules for multiQC. (these are all todo...)

The easiest way to run all of qckitalign's diagnostics is with the wrapper qckitalign, which will execute all of the diganostic functions in this package on a single BAM/SAM file. To run on multiple files, run multiqckitalign. Individual functions can be run as well, please consult the documentation for how to run them individually.

This vignette runs through all of the diagnostic functions on sample data to give an idea of qckitalign's capabilities.

## Basic diagnostics

Can give bam length...


## Basic alignment rates



The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
